Classless Java: Tuning Java Interfaces

### 2015-12-07 paper/sections/RelatedWork.tex
scala virtualized
sqlalchemy ref

Scala-Virtualized~\cite{}\bruno{reference!} is an extension to Scala, 
which allows blending shallow and deep embedding of DSLs. It redefines 
some of Scala's language constructs to method calls, 
which can be overridden by DSL implementors. Thus Scala Virtualized  
can also reinterpret syntax, and be seen as a form of language tuning. 
However, although many Scala's language constructs are supported, 
not all language constructs can be virtualized.

@@

When the base language has a flexible enough syntax and a fast and
powerful enough reflection mechanism, we may just need to play with
operator overloading and other language tricks to discover that the
language feature we need can be expressed as a simple library in our
language. An example of this is SQLAlchemy\cite{}\bruno{reference} in
Python, which ...\bruno{does what? describe what SQLAlchemy is}
without requiring any syntactic extensions to Python.
Java-like languages tend to sit in the middle of two extremes:
libraries can not influence the type system, so many solutions valid
in Python or other dynamic languages are not applicable, or have the
cost of losing type-safety.

>>>>

Scala-Virtualized~\cite{Rompf2012scalavirtualized} is an extension to Scala, 
which allows blending shallow and deep embedding of DSLs. It redefines 
some of Scala's language constructs to method calls, 
which can be overridden by DSL implementors. Thus Scala Virtualized  
can also reinterpret syntax, and be seen as a form of language tuning. 
However, although many Scala's language constructs are supported, 
not all language constructs can be virtualized.

@@

When the base language has a flexible enough syntax and a fast and
powerful enough reflection mechanism, we may just need to play with
operator overloading and other language tricks to discover that the
language feature we need can be expressed as a simple library in our
language. An example of this is SQLAlchemy\cite{bayer2012sqlalchemy} in
Python, which uses operator overloading to dynamically turn normal python expressions into database queries
without requiring any syntactic extensions to Python.
Java-like languages tend to sit in the middle of two extremes:
libraries can not influence the type system, so many solutions valid
in Python or other dynamic languages are not applicable, or have the
cost of losing type-safety.
